Data Management for LSST Special Programs

### 2024-03-26 sec_intro.tex
fix typo
update summary, labels text

\section{Memoranda} \label{sec:mem}

The three memoranda for Rubin Data Management regarding Special Programs are:

@@

\item All visits should have a region label \textit{and} an observing mode
label, and these labels should be propagated to processed images and catalog data.
(Section~\ref{ssec:sci_labels})

\item Special Processing should be done by Rubin Data Management to 
produce unique and separate data products
for Special Programs when it is both possible and necessary.
(Section~\ref{ssec:sci_sproc}).

@@

Based on Right Acension and Declination.

To be applied to data by Rubin Data Management, e.g., using a look-up table.

Region labels would include, e.g., WFD low-dust, Galactic Plane, Galactic 
Bulge, SCP, NES, or Virgo; DDF fieldname; mini-survey region name.

@@

Based on the scheduler mode at the time of the observation
(i.e., survey cadence or strategy).

To be applied by the Survey Scheduler team via the observations scheduler.

Observing mode labels might include, e.g., WFD, DDF, TOO, mini-survey name, or other 
options like engineering, commissioning, and director's discretionary.

@@

Examples of Special Processing include the processing
of images with non-standard exposure times, images obtained
during twilight, or nightly stacking and differencing
of images in deep drilling fields.
See \Section~\ref{ssec:proc_special} for more detailed examples of Special Processing.

>>>>

\section{Summary} \label{sec:mem}

The three main takeaways for Rubin Data Management regarding Special Programs are:

@@

\item All visits should have a region label \textit{and} an observing mode
label, and these labels should be available to users as query constraints for
all images and tables.
(Section~\ref{ssec:sci_labels})

\item Special Processing should be done by Rubin Data Management to
produce unique and separate data products for Special Programs in
certain cases that meet specific definitions of "possible and necessary".
(Section~\ref{ssec:sci_sproc})

@@

Applied to a visit based on its Right Acension and Declination (Section~\ref{ssec:sci_labels}).

@@

Applied to a visit based on the scheduler mode at the time of the observation,
i.e., survey cadence or strategy (Section~\ref{ssec:sci_labels}).

@@

Examples of Special Processing include the processing
of images with non-standard exposure times, images obtained
during twilight, or nightly stacking and differencing
of images in deep drilling fields.
See Section~\ref{ssec:proc_special} for more detailed examples of Special Processing.
